Manuscript Figures for Genome Biology

### 2018-08-30 manuscript_figures/manuscript_figures.Rmd
Add figure to compare pi0 settings in yeast

>>>>

## Figure contrasting FDR results in different yeast simulation settings

```{r Figure2, fig.width = 10, fig.height = 8}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[(grepl("yeast-", objects) | grepl("yeastH-", objects)) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)] 
labs <- rep("2000 Differentially expressed genes", 2)
labs[grepl("H", resfile)] <- "500 Differentially expressed genes"
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

plist <- vector("list", length(resfile))
for (l in seq_along(resfile)){

  de5 <- readRDS(file=resfile[l])
  res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

  # Fdr by alpha
  p1 <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
                ggtitle("")

  # tpr by alpha
  p2 <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) + 
                theme(legend.position = "none") + 
                ggtitle("")

  if (l == 1){
    leg <- get_legend(p1)
  }
  p1 <- p1 + theme(legend.position = "none")

  plist[[l]] <- plot_grid(p1, p2, ncol = 2, 
                   labels = c("", labs[l]), label_x = -0.65 )
}

# combine rows into one figure
Fig <- plot_grid(plotlist = plist, nrow = 2, 
                 labels = LETTERS[1:2], label_size = 20)
Fig <- plot_grid(Fig, leg, ncol = 2, rel_widths = c(1, 0.2))
Fig
ggsave(file.path(outdir, "Figure_yeast_varyingpi0.pdf"), width=10, height=8)
